%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} 

\usepackage{xcolor}
\definecolor{darkcerulean}{rgb}{0.03, 0.27, 0.49}

\usepackage[colorlinks=true,allcolors=darkcerulean]{hyperref}

%\hypersetup{
  %  colorlinks=true,
  %  linkcolor=black,
  %  filecolor=magenta,      
  %  urlcolor=darkcerulean,
  %  pdftitle={},
  %  pdfpagemode=FullScreen,
 %   }

\usepackage{fancyhdr}% Create header
\pagestyle{headings}
\markright{\hfill \hfill Conevska CV, p. }% Put header to the right

\usepackage{enumitem}% http://ctan.org/pkg/enumitem
\setlength{\parindent}{0pt}


\usepackage[left=0.75in,top=1.2in,right=0.75in,bottom=0.6in]{geometry}%Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{\LARGE A\MakeLowercase{leksandra} C\MakeLowercase{onevska} }  

\address{aleksandraconevska@g.harvard.edu} 

\address{Website: www.aleksandraconevska.com}

\begin{document}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{\Large E\MakeLowercase{ducation}}

{\bf Harvard University} \hfill {\em } 

Ph.D Government (2020 - ) \hfill { } 
\NewEntry{}
{\vspace{-\baselineskip}
\begin{itemize}[topsep=0pt]
\medskip
    \item[] \textit{Committee:} James M. Snyder, Jr., Dustin Tingley, Gary King, Jeffry Frieden 
   \item[] \textit{Affiliations:} Institute for Quantitative Social Science, Center for American Political Studies (CAPS), the Weatherhead Climate Change Cluster


\end{itemize}
}

\bigskip

{\bf McGill University} \hfill {\em } 


Master of Arts, Political Science, 2019 \hfill { } 
\NewEntry{}
{\vspace{-\baselineskip}
\begin{itemize}[topsep=0pt]
 \medskip
  \item[] Thesis: ``International Cooperation and Natural Disasters: Evidence from Trade Agreements"
    \vspace{-\baselineskip}
     \medskip
  \item[] Supervisors: Leonardo Baccini, Krzysztof J. Pelc (second reader)
      \vspace{-\baselineskip}
     \medskip


\end{itemize}
}
\medskip
\smallskip

Bachelor of Arts \& Science, \textit{Distinction}, 2017
\NewEntry{}
{
\vspace{-\baselineskip}
\medskip
\begin{itemize}[topsep=0pt]
  \setlength\itemsep{-0.7em}
  \item[] Joint Honours Environmental Science and Political Science
  \item[] Honours Thesis: ``Trade and Environmental Shocks", Supervisors: Leonardo Baccini, James Ford

\end{itemize}
}




\end{rSection}

\bigskip

\begin{rSection}{\Large  P\MakeLowercase{ublications}} \itemsep -3pt {}
\vspace{-0.7cm}

\item Kuriwaki, S., Reece, M., Baltz, S. et al. (2024). \href{https://doi.org/10.1038/s41597-024-04017-1}{Cast vote records: A database of ballots from the 2020 U.S. Election}. Nature Scientific Data 11, 1304.
\medskip

\item Conevska, A. (2021). International Cooperation and Natural Disasters: Evidence from Trade Agreements. \textit{International Studies Quarterly},  65(3), 606-619.
\medskip

\item Mikkelson, G. M., Avidan, M., Conevska, A., & Etzion, D. (2021). Mutual reinforcement of academic reputation and fossil fuel divestment. \textit{Global Sustainability}, 4.
\medskip

\item Conevska, A., & Urpelainen, J. (2020). Seasonal Variation in Electricity Consumption Among Off-Grid Households: Evidence from Rural India. \textit{ Energy Research \& Social Science, 65}, 101444. 
\medskip

\item Conevska, A., Ford, J., & Lesnikowski, A. (2020). Assessing the adaptation fund’s responsiveness to developing country’s needs. \textit{Climate and Development, 12(5),} 436-447. 
\medskip

\item Conevska, A., Ford, J., Lesnikowski, A., & Harper, S. (2019). Financing for food system adaptation to climate change: an analysis of UNFCCC-related funds. \textit{Climate Policy, 19(1)}, 43-58. 
\begin{itemize}
    \item Cited in the Intergovernmental Panel on Climate Change (IPCC) Report.
\end{itemize}



\end{rSection}

\newpage

\begin{rSection}{\Large W\MakeLowercase{orking} P\MakeLowercase{apers}} \itemsep -3pt {}
\vspace{-0.7cm}

 
\item \href{https://osf.io/preprints/osf/db3mj}{How Partisan are U.S. Local Elections? Evidence from 2020 Cast Vote Records.} (with Shigeo Hirano, Shiro Kuriwaki, Jeffery B. Lewis, Can Mutlu, and James M. Snyder, Jr.). \textit{R\&R}.

\medskip

\item When Do Voters Stop Caring? Estimating the Shape of Voters' Utility Functions (with Can Mutlu). \textit{R\&R}.

\medskip

\item Partisanship and Voting (with Shigeo Hirano, Can Mutlu, and James M. Snyder, Jr.)

\medskip 

\item When Are Parties `Good' For The Environment?  (with Can Mutlu)


\medskip

\item Polluting Politicians: Import Shocks and Environmental Outcomes (with Sean Nossek)

\end{rSection}

\bigskip


\begin{rSection}{\Large W\MakeLowercase{ork} I\MakeLowercase{n} P\MakeLowercase{rogress}} \itemsep -2pt {}
\vspace{-0.7cm}


\item Generation Green New Deal? Social Norms, Rebellion, and Pro-Climate Behavior

\medskip

\item Elected Electricity Regulators and the
Energy Transition

\medskip


\item Financial Vulnerability and Climatic Shocks: Evidence from Novel Customer and Business Data (with Saika Belal \& Michael Hiscox)

\medskip
\item Do Consumer Decarbonization Incentives Catalyse Analogous Public Sector Incentives? Uptake of Consumer Decarbonization Incentives and Public Policy (with Saika Belal \& Michael Hiscox)

\end{rSection}

\bigskip



\begin{rSection}{\Large F\MakeLowercase{ellowships and}  A\MakeLowercase{wards}} \itemsep -2pt
\vspace{-0.7cm}
\item Predoctoral Fellowship Harvard STAR Lab \$50,000/year, 2024-2025
\item SSHRC Canada Doctoral Fellowship 60,000 CAD, 2023-2025 
\item Fulbright Scholarship \$20,000, 2018-2019
\item SSHRC Canada Master's Graduate Scholarship 17,500 CAD, 2018-2019 
\item Michael Smith Foreign Study Scholarship 6,000 CAD, 2018-2019
\item McGill Undergraduate Scholarship 32,000 CAD, 2013-2017
\item Teaching Assistant of the Year, McGill University, 2017-2018
\end{rSection}

\bigskip


\begin{rSection}{\Large G\MakeLowercase{rants}} \itemsep -2pt
\vspace{-0.7cm}
\item The Institute for Quantitative Social Science Travel Grant Award at Harvard \$1000, 2023
\item The Institute for Quantitative Social Science Research Grant at Harvard \$3000, 2023
\item The Institute for Quantitative Social Science Travel Grant Award at Harvard \$1000, 2022
\item The Institute for Quantitative Social Science Research Grant at Harvard \$3000, 2021
\end{rSection}


\newpage

\begin{rSection}{\Large T\MakeLowercase{eaching}} \itemsep -2pt
\vspace{-0.7cm}

\item \textbf{Harvard University} 
\item TF, ``GOV 2001. Quantitative Social Science Methods" Professor Gary King. Fall 2022
\medskip
\item TF, ``GOV 1722. Politics of the Environment and Climate Change" Professor Steve Ansolabehere and Professor Dustin Tingley. Spring 2022 \& Spring 2023


\item \textbf{McGill University} 
\item TA, ``POLI 445: International Political Economy, Monetary Relations" Professor Mark Brawley. Fall 2017


\medskip

\item TA, ``POLI 666: Advanced Quantitative Methods" Professor Leonardo Baccini. Winter 2018

\medskip
\item TA, ``POLI 666: Advanced Quantitative Methods Causal Inference" Professor Leonardo Baccini. Winter 2019

\end{rSection}

\bigskip 

\begin{rSection}{\Large R\MakeLowercase{eferee} S\MakeLowercase{ervice}} \itemsep -2pt
\textit{Climate Policy, Energy and Social Science Research, Climate and Development, Challenges in Sustainability, American Political Science Review}
\end{rSection}

\bigskip

\begin{rSection}{\Large S\MakeLowercase{ervice}} \itemsep -2pt
\vspace{-0.7cm}
\item Climate Pipeline Project Graduate Student Organizer (2022-present)

\item Harvard Experiments Working Group 2024 Conference Organizer (2024)

\item Harvard 2023 Poster Session Coordinator (2022-2023)

\item Graduate Political Economy Research Workshop Coordinator (2021-2022)

\end{rSection} 




\bigskip

\begin{rSection}{\Large C\MakeLowercase{onferences and} I\MakeLowercase{nvited} P\MakeLowercase{resentations}} \itemsep -2pt
\vspace{-0.7cm}
\item Weatherhead Center’s annual Advisory Committee Meeting (Presentation, invited)
\item Climate Pipeline Project Conference Harvard 2024 (Organizer and Presentation)
\item Weatherhead Spotlight 2024: Climate Change Research Cluster (Presentation, invited)
\item Weatherhead Spotlight 2023: STAR Lab and Businesses Creating Positive Environmental Impacts
\item Annual Meeting of the American Political Science Association 2023 (Presentation)
\item Climate Pipeline Project Workshop Harvard 2022 (Organizer and Presentation)
\item Annual Meeting of the American Political Science Association 2022 (Presentation)
\item  Climate, Justice, Resilience in A Rapidly Warming World, Radcliffe Institute 2022 (Talk, invited) 
\item Climate Pipeline Project Conference Brown University 2021 (Presentation)
\item Scotia Group COP26 Forum 2022 (Talk, invited)
\item Scotia Group Weatherhead Center Climate Dialogue 2021 (Talk, invited)
\item McGill Climate Conference 2019 (Organizer) 
\item European Climate Change Adaptation Conference 2019 (Presentation)
\item Understanding International Economic Agreements The Hebrew University 2019 (Presentation)
\item Environmental Policy and Governance Conference 2018 (Presentation)
\item Duck Family Workshop University of Washington 2018 (Presentation)
\item Conference on Economies in an Age of Limits 2017 (Presentation) 
\item McGill Political Science Research Brunch 2018 (Presentation)
\end{rSection}


\bigskip

\begin{rSection}{\Large  E\MakeLowercase{xperience}}

\begin{rSubsection}{Harvard Fellows at the Forefront}{May - August 2021; May - August 2022}{Graduate Research Organizer}{}
\item Lead a team of Undergraduate Research Assistants alongside Professor Dustin Tingley. 
\item Developed research project on inter-generational climate change mobilization. 
\item Guided research team, set agenda, and organized research team daily tasks.
\end{rSubsection}

\begin{rSubsection}{London Economics International LLC}{November 2019 - July 2020}{Consultant}{}
\item  Advising public and private sector clients on renewable and conventional energy policy, market and tariff design and asset valuation. 
\item Modelling regional electricity markets, updating demand assumptions for a 10-year price forecast.
\item Formulating briefing memos for the President of LEI for expert testimony preparation and supporting preparation of numerous proposals for projects.
\end{rSubsection}

\begin{rSubsection}{World Bank Group (WBG)}{May 2018 - September 2018}{Consultant}{}
\item Developed 2018 WBG Action Plan on Climate Change and presented to 30+ top WBG officials. 
\item Created methodology to identify clean energy and adaptation strategies for international stakeholders.
\item Analyzed key adaptation interventions to identify focal lessons learned for future adaptation planning.
\end{rSubsection}

\begin{rSubsection}{Siemens Ltd}{December 2017 - May 2018}{Economic Policy and Regulatory Intern}{}
\item Developed an analysis of low emission policies and regulations and presented it to key stakeholders.
\item Created framework to assess economic determinants of energy transitions in multiple national contexts. 
\item Assessed feasibility of multi-source energy integration in various geographical contexts.  
\end{rSubsection}

\end{rSection}

\bigskip

\begin{rSection}{\Large S\MakeLowercase {kills and} T\MakeLowercase{echnical} S\MakeLowercase{trengths}}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages &  R,RStudio, STATA \\
Software \& Tools &  LaTeX, Github, ArcGIS \\
Language Skills & Fluent English, Bosnian, Croatian, Serbian. French (Beginner)
\end{tabular}

\end{rSection}


\end{document}

